Preliminary categorisation of SpaceWarps candidates

### 2016-04-08 paper2.tex
more refs
compile without errors

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

@@

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols

@@

\newcommand{\inclfig}[2]{
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input.png}
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1.png}
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol.png}
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2.png}
  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot.png}
}

\newcommand{\lenstitle}[1]{\noindent\textit{#1}\quad}

@@

% Abstract of the paper
\begin{abstract}

%This is a simple template for authors to write new MNRAS papers.
%The abstract should briefly describe the aims, methods, and main results of the paper.
%It should be a single paragraph not more than 250 words (200 words for Letters).
%No references should appear in the abstract.
\end{abstract}

@@

@@

The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution (Keeton, 2002).
This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.

@@

\begin{figure}
	\inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[fleqn,usenatbib]{mnras}

@@

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}

@@

% Only include extra packages if you really need them. Common packages are:
\usepackage[dvipdfmx]{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{bmpsize}

@@

\newcommand{\inclfig}[2]{
  \centering
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_input} %
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img1} \\
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img3_ipol} %
  \includegraphics[width=0.49\linewidth]{spaghetti/#2_img2} \\
  \includegraphics[width=1\linewidth]{masses/#1_#2_mstel_vs_mtot}
}

\newcommand{\lenstitle}[1]{\noindent\textit{#1} --}

@@

% Abstract of the paper
\begin{abstract}
This is a simple template for authors to write new MNRAS papers.
The abstract should briefly describe the aims, methods, and main results of the paper.
It should be a single paragraph not more than 250 words (200 words for Letters).
No references should appear in the abstract.
\end{abstract}

@@

Here we cite \cite{2015MNRAS.447.2170K}.

@@

The parameterised model function was obtained from the gravitational potential of an isothermal ellipsoid mass distribution \cite{2001astro.ph..2340K}.
This model is frequently used to describe gravitational lenses as it tends to fit well with observations.
The isothermal ellipsoid model outputs three useful parameters: the radius of the Einstein ring, the ellipticity of the model and the angle of the ellipticity from the vertical, giving the orientation of the galaxy.
By applying this model to simulated lenses for which the values of these parameters were already known, it was possible to gain an estimate of the projected accuracy of the results, before applying the model to the candidate lensing galaxies.

@@

\begin{figure}
  \inclfig{SW58}{ASW0007iwp_4XBJWT3COV}
  \caption{}
\end{figure}
